Adopting agile in the large: motivations, success factors and challenges

### 2014-04-28 journal/article.tex
Managing change

\subsubsection{Challenges caused by management of the transformation}

@@

% ---------------------------------------------------------------------

>>>>

\subsubsection{Leadership challenges in the transformation}

@@

* Other problems with leading change

[P43]  Failing to set goals

Our greatest failures have occurred during instances where we have not set down
widely-communicated expectations.  We attempted to compel test-driven
development through the scrum teams during our third and fourth agile releases.
We failed, though, to set down precisely what our expectations were for our
development teams and to police and reward or correct developers based on
results.  As such, we had very spotty results with TDD, with some teams
succeeding in implementing it, but most not meeting with the level of success
for which we had hoped.  We set up a practice where we asked teams to create
User Acceptance Testing criteria, to guide development and UAT, but we stopped
enforcing it after a few iterations. Product Owners started delivering feedback
that UATs were becoming less focused and far less productive. We now strongly
recommend them for all teams.

In a couple of teams we let ill-defined user stories into an iteration, with
disastrous results.  Small stories dragged on for weeks because we hadn’t
defined their scope.  When we missed retrospectives, we found that small
problems would start to spiral.  When we didn’t fully populate five iterations
of a release with user stories at the Release Planning Meeting we found
important pieces of functionality getting deprioritized and missing the release
date. When we missed updating our metrics, the teams lost focus on the end goal.

[P40]  People do not speak their minds

at the outset most meetings seemed productive, since we had a lot of nodding 
heads and everyone stepped out of meetings in agreement. However, I soon
realized that any visible agreements on an approach or direction at meetings did
not always mean that the participants  supported the decision. Therefore,
drawing out an implementation  plan based on any key decisions emerging from
meetings would be futile.

Most 'real' discussions and communication  of how people really felt about a
direction  or decision happened outside of meetings. The undercurrents  of
resistance or genuine concerns that people had were never voiced at meetings.
Direct conversation and sharing feedback was further constrained when the
meetings included senior management representatives.

Given  the  organization's   passive-aggressive culture there was no doubt in my
mind that the transition to agile required a mind shift, but I also recognized
that mind shifts couldn't happen overnight.
% ---------------------------------------------------------------------
